---
title: "homework"
author: "quyaran"
date: "2020/3/28"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## abstract:This report considers approximation of the distribution function of $N(0, 1)$ by the Monte Carlo methods.

## Math Equation

In this problem, i consider approximation the distribution
function of  $N(0,1)$ , 
\begin{align}
    \Phi(t) = \int_{-\infty}^t\frac{1}{\sqrt{{2\pi}}}e^
     {(-y^2)/2} \,{\rm d}y,
\end{align}
by the Monte Carlo methods:
\begin{align}
    \hat{\Phi}(t) = \frac{1}{n}\sum_{i=1}^n I(X_i \leq t),
\end{align}
where $X_i$ is a random sample from $N(0,1)$, and $I(.)$ is 
the indicator function.
Experiment with the approximation at
$n \in \{10^2, 10^3, 10^4\}$ at
$t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$ to
form a table.

## Table

The approximation results are shown in the table.

```{r norm, echo = TRUE }
t=c(0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=c(100,1000,10000)
p=matrix(0,nrow=9,ncol=3)
#a=0
for (i in 1:9)
  for(j in 1:3){
    #a=a+1
    num=rnorm(n[j],0,1)
    p[i,j]=mean(num<t[i])
    #print(a)
  }
rownames(p)<-t
colnames(p)<-n
true_value<-c(pnorm(0),pnorm(0.67),pnorm(0.84),pnorm(1.28),pnorm(1.65),
           pnorm(2.32),pnorm(2.58),pnorm(3.09),pnorm(3.72))
p<-cbind(p,true_value)
p<-round(p,digits=3)
#make figure more beautiful
library(knitr)
library(magrittr)
library(kableExtra)
kable(p, booktabs=TRUE, caption='(ref:the results)') %>%
  kable_styling(bootstrap_options = "striped",full_width = F) %>% 
 column_spec(1,bold=T)#full_width=F, is or isn't full of screen

```

## Figure 

After repeat the experiment 100 times, I draw box plots of the 100 approximation errors at each $t$ using **ggplot2** for each $n$. 

<div align=center>
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom1_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom2_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom3_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom4_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom5_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom6_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom7_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom8_png)
[Caption for the picture.](C:/Users/jx/Desktop/plot/plot_zoom9_png)

## Explaination
In the section Table, i generete one table to describe the 
difference between approximation and true value. The results show that the error decreases with the increase of the number of samples.And in the section figure, it proves once again that this includes. At the same time, we can see that when the number of samples increases, the extreme value decreases. 
Especially, when t=3.09, n=100 or t=3.72, n=100, 1000, the errors are almost 0.

&emsp;&emsp;[Reference website：https://github.com/data-science-in-action/03-practicing-r-markdown-dcddingchendong]